Analysis of H-1B Visa Workers Using H-1B LCA Disclosure Data (2020–2024)

### 2025-01-31 products/manuscript/Manuscript.qmd
commit

## General Background Information
_Provide enough background on your topic that others can understand the why and how of your analysis_
H-1B is a nonimmigrant visa category that allows employers to hire foreign workers in specialty occupations, like methematics, engineering, technology, and medical sciences [H1BVisaProgram2016]. It requires the employee to have a bachelor's degree or equivalent in the specific specialty. Typically, the maximun duration of an H-1B visa is six years.It is the most common work visa in the US. There are 65,000 available H-1B visas each year, with 20,000 additional visas for candidates with a master's or doctorate degree from a U.S. institution. If there are more than 65,000 applications, USCIS will run a lottery to decide who can file an H-1B petition. As USCIS is receiving more and more H-1B registration these years, it's harder for a foreign worker to get an H-1B visa. The Labor Condition Application (LCA) is an application filed by employers to apply for work authorization on behalf of employees as a prerequisite for H-1B [LaborConditionApplication2025]. The LCA contains essential details such as job title, wage, and location about the proposed H-1B employment. Therefore, analyzing the LCA data can provide some ideas on the H-1B application status.

>>>>

## General Background Information
_Provide enough background on your topic that others can understand the why and how of your analysis_
H-1B is a nonimmigrant visa category that allows employers to hire foreign workers in specialty occupations, like methematics, engineering, technology, and medical sciences [@H1BVisaProgram2016]. It requires the employee to have a bachelor's degree or equivalent in the specific specialty. Typically, the maximun duration of an H-1B visa is six years.It is the most common work visa in the US. There are 65,000 available H-1B visas each year, with 20,000 additional visas for candidates with a master's or doctorate degree from a U.S. institution. If there are more than 65,000 applications, USCIS will run a lottery to decide who can file an H-1B petition. As USCIS is receiving more and more H-1B registration these years, it's harder for a foreign worker to get an H-1B visa. The Labor Condition Application (LCA) is an application filed by employers to apply for work authorization on behalf of employees as a prerequisite for H-1B [@LaborConditionApplication2025]. The LCA contains essential details such as job title, wage, and location about the proposed H-1B employment. Therefore, analyzing the LCA data can provide some ideas on the H-1B application status.
